---
title: "ggplot time hw"
output: html_document
---

Problem 1) Using the rwunderground package (you will need to request an api key per the instructions in the lecture), display a graph as provided in the PowerPoint showing the difference between the high and low temperatures for Dallas, Texas for each day (note: the actual dates can vary since the forecast of ten days varies by when the homework is completed).
```{r dates with weather via API}

library(ggplot2)
library(rwunderground)

rwunderground::set_api_key("acd87771c451eaa8") #API key

WUNDERGROUNDID = 'acd87771c451eaa8' 

library(lubridate)     # tidyverse package for date manipulation (using function mdy)
library(quantmod)      # includes zoo (masks as.Date from base R), xts; used for getSymbols 
library(scales)        # For axis date formatting via labels
library(broom)         # use function tidy to create data frame from lists
library(tidyr)         # tidyverse package for data frame/tibble manipulation (using function spread)
library(dplyr)         # Used for filter
library(blscrapeR)     # retrieve Bureau of Labors stats via bls_api function


#custom function used to format axes labels with degree word for temperatures
degrees <- function(x) {
  paste(x, "degrees",sep = "  ")
} 

forecastDallas = forecast10day(set_location(territory = "Texas", city = "Dallas"))
head(forecastDallas)
str(forecastDallas) 
forecast.p <- ggplot(forecastDallas, aes(x = date))
forecast.p  + 
  geom_line(aes(y = temp_high - temp_low), color = 'coral1') + 
  scale_x_datetime(name = 'Dates', labels = date_format("%b/%d/%Y")) +  
  scale_y_continuous(name = 'Temperatures', labels = degrees, breaks = c( 17.5, 20, 22.5, 25, 27.5)) + 
  theme(axis.text.x=element_text(angle = -90, hjust=1),axis.text.y=element_text(angle = 45, hjust=1))  

```

Problem 2) We will project the stock prices for AT&T (T symbol) and Toyota (TM symbol) via the quantmod package (using the same function as in the lecture). Read stock data for AT&T and Toyota for dates from January 1 to September 30 2017. Create a plot using ggplot identical to the graph provided in the PowerPoint, with AT&T Graph the AT&T and Toyota open prices over the data ranges of January 1 2017 to December 31 2020. Using smooth geoms with a regular linear model, project the prices through the entire date range of the graph.
```{r stock data and exponential growth}

stock_data <- getSymbols(c("T","TM"),src='yahoo', from = "2017-01-01", to = "2017-09-30")
head(stock_data)

ATnT <- fortify(T) 
Toyota <- fortify(TM)

ggplot() + 
  geom_line(data = ATnT, aes(x = Index, y = T.Open),color = "cyan1")+
  geom_smooth(data = ATnT ,aes(x=Index, y = T.Open), color = "coral1", method = "lm", fullrange = TRUE)+
  geom_line(data = Toyota,aes(x = Index, y = TM.Open), color = "coral1")+
  geom_smooth(data = Toyota, aes(x = Index, TM.Open), color = "coral1", method = "lm", fullrange = TRUE )+
  scale_x_date(name = "Dates", limits  = c(as.Date("2017-01-01"), as.Date("2021-01-01"))) +
  scale_y_continuous(name = 'Open',limits  = c(1, 125))
```
